### 2019-01-07 fe_px_paper/fe_body_text.tex
Added discussion of possible Fe monitor reactions

Using the final proton fluence at each energy position, cross sections for \ce{^{48}Cr}, \ce{^{48}V},  \ce{^{49}Cr}, \ce{^{51}Mn}, \ce{^{51}Cr},  \ce{^{52}Fe}, \ce{^{52m}Mn}, \ce{^{52g}Mn}, \ce{^{52}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Mn}, \ce{^{56}Co}, \ce{^{57}Co}, \ce{^{58m}Co}, \ce{^{58g}Co}, and \ce{^{58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{60}Co}, \ce{^{60}Cu}, \ce{^{61}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K}, \ce{^{44g}Sc}, \ce{^{44m}Sc}, \ce{^{44}Sc}, \ce{^{47}Sc}, and \ce{^{48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).

@@

\textred{Placeholder text follows...fill in actual discussion of results...}

@@

These results have several notable features.
The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.

% Furthermore, t
This work presents the first measurements of several observables in 
% these mass regions.
% This work reports the first experimental measurement of
this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
% It also represents  the first measurement of 
the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
% (${^{1}/_{2}}^{-}$)
% ($\sfrac{1}{2}^-$) 
isomer branching ratio via \ce{^{nat}Nb}(p,x).

>>>>

Using the final proton fluence at each energy position, cross sections for \ce{^{48}Cr}, \ce{^{48}V},  \ce{^{49}Cr}, \ce{^{51}Mn}, \ce{^{51}Cr},  \ce{^{52}Fe}, \ce{^{52m}Mn}, \ce{^{52g}Mn}, \ce{^{52}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Mn}, \ce{^{56}Co}, \ce{^{57}Co}, \ce{^{58m}Co}, \ce{^{58g}Co}, and \ce{^{58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{60}Co}, \ce{^{60}Cu}, \ce{^{61}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K}, \ce{^{44g}Sc}, \ce{^{44m}Sc}, \ce{^{44}Sc}, \ce{^{47}Sc}, and \ce{^{48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).

@@

% \textred{Placeholder text follows...fill in actual discussion of results...}

@@

These results have several notable features.
The various \ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.

% Furthermore, t
This work presents the first measurements of several observables in 
% these mass regions.
% This work reports the first experimental measurement of
this mass region, including the \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
% It also represents  the first measurement of 
the independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).  
The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr},\ce{^{52g}Mn},\ce{^{58g}Co} cross sections.
% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
% (${^{1}/_{2}}^{-}$)
% ($\sfrac{1}{2}^-$) 
% isomer branching ratio via \ce{^{nat}Nb}(p,x).

% \textred{Comment on possible monitor reactions  here...}

Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe} \cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target. 
It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and lifetime. 
Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr} \cite{Dong2014}) has a convenient lifetime and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
